lifespan_eda

### 2024-06-06 eda/lifespan_eda.Rmd
lots of supplemental plots

```{r}
skim(cn.df.unique)
levels(cn.df.unique$study)
```

@@

Removed `r nrow(cn.df.unique) - nrow(cn.df.eulerfilt2)` subjects, `r nrow(cn.df.eulerfilt2)` remain

>>>>

```{r}
skim(cn.df.unique)
levels(cn.df.unique$study)
n_unique(cn.df.unique$study)
```

@@

Removed `r nrow(cn.df.noinf) - nrow(cn.df.eulerfilt2)` subjects, `r nrow(cn.df.eulerfilt2)` remain
